Output Summary

### 2020-09-09 03-post-process/output-plots.Rmd

>>>>

# MCMC Information {.tabset .tabset-pills}

## Attributes

This table shows some dimensions of the MCMC run.

```{r mcmc-dims}
# query the dimensions of the posterior samples
dims = post_dim(post)

# build a data frame for printing
df = data.frame(Quantity = c("Burn-in + Adapt Iters", "Post Burn-in Iters", "Thinning Interval", "Chains", "Saved Iters", "Monitored Quantities"), Value = unname(dims))

# render the table
kable(df, format.args = list(big.mark = ",")) %>%
  kable_styling(full_width = F, bootstrap_options = "condensed")
```

## Diagnostic Summaries

This table shows the number of parameters that fail to meet some diagnostic threshold. Lower Rhat values are good, larger Neff values are good, and lower MCMC SE/Mean values are good.

The "match" column shows the kinds of parameters summarized in that row. E.g., `^mu_phi` covers all parameter names that start with `mu_phi` and are followed by anything else (`r paste(match_params(post, "^mu_phi"), collapse = ", ")`).

This model was ran for a very short time, and I'm impressed with how well the sampling performed even considering this.

```{r mcmc-diags}
# groups of parameters to match and calculate diagnostic summaries for separately
diag_params = list(
  c("alpha", "beta", "sigma_Pb"),
  "^mu_phi",
  "^mu_psi",
  "^mu_omega",
  "^mu_pi",
  "^sig_Lphi",
  "^sig_Lpsi",
  c("^sig_Lomega", "^sig_Lpi"),
  "^Pb[", 
  "init_recruits", 
  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]"
)

# calculate the diagnostic statistics for each group
diags = lapply(diag_params, function(param) post_summ(post, param, Rhat = T, neff = T, mcse = T)[c("mean", "Rhat", "neff", "mcse_mean"),])

# count up the number of parameters by group that fail to meet certain thresholds
diag_summ = t(sapply(diags, function(param) {
  mc_cv = (param["mcse_mean",]/param["mean",]) * 100
  c(
    n_total = ncol(param),
    n_Rhat_1 = sum(param["Rhat",] > 1.05),
    n_Rhat_2 = sum(param["Rhat",] > 1.1),
    n_Rhat_3 = sum(param["Rhat",] > 1.2),
    n_neff_1 = sum(param["neff",] < 2000),
    n_neff_2 = sum(param["neff",] < 1000),
    n_neff_3 = sum(param["neff",] < 500),
    mc_cv_1 = sum(mc_cv > 1),
    mc_cv_2 = sum(mc_cv > 5),
    mc_cv_3 = sum(mc_cv > 10)
  )
}))

# format to a table
diag_summ = as.data.frame(diag_summ)
colnames(diag_summ) = c("Total Params", ">1.05", ">1.1", ">1.2", "<3000", "<1000", "<500", ">1%", ">5%", ">10%")
df = cbind("Match" = unlist(lapply(diag_params, paste, collapse = ", ")), diag_summ)

# render the table
kable(df, align = "lcccccccccc") %>%
  kable_styling(full_width = F, bootstrap_options = c("condensed", "striped")) %>%
  add_header_above(c(" " = 2, "Rhat" = 3, "Neff" = 3, "MCMC SE/Mean * 100%" = 3)) %>%
  column_spec(1, monospace = T) %>%
  column_spec(c(2,5,8), border_right = T)

```
